---
title: "Part 2"
output: pdf_document
---

```{r}
install.packages('forecast', dependencies = TRUE)
library(forecast)
library(zoo)
library(ggplot2)
install.packages('readr')
library(readr)
library(xts)
library(dplyr)
install.packages('fpp')
library(fpp)
install.packages('fpp3')
library(fpp3)
install.packages('gridExtra')
library(gridExtra)
install.packages('ranger')
library(ranger)
install.packages('ftsa')
library(ftsa)
install.packages('randomForest', dependencies = TRUE)
library(randomForest)
install.packages('corrplot', dependencies = TRUE)
library(corrplot)
install.packages('vars', dependencies = TRUE)
library(vars)
```


```{r}

Projectdata <- read.csv("C:\\Users\\anura\\Downloads\\Projectdata.csv")
head(Projectdata)

tsdata <- xts(Projectdata[,2:19],as.Date(Projectdata$ï..date))
head(tsdata)

```


Part 1 
Store level aggregation is needed for this part
Each store has one Hobbies, two Households and 3 Foods
```{r}
Store_CA_1$store_1=tsdata$Hobbies_CA_1+tsdata$Household_1_CA_1+tsdata$Household_2_CA_1+tsdata$Foods_1_CA_1+tsdata$Foods_2_CA_1+tsdata$Foods_3_CA_1
Store_CA_2$store_2=tsdata$Hobbies_CA_2+tsdata$Household_1_CA_2+tsdata$Household_2_CA_2+tsdata$Foods_1_CA_2+tsdata$Foods_2_CA_2+tsdata$Foods_2_CA_2
Store_CA_3$store_3=tsdata$Hobbies_CA_3+tsdata$Household_1_CA_3+tsdata$Household_2_CA_3+tsdata$Foods_1_CA_3+tsdata$Foods_2_CA_3+tsdata$Foods_3_CA_3


Store_CA_1<-Store_CA_1[,2]
Store_CA_2<-Store_CA_2[,2]
Store_CA_3<-Store_CA_3[,2]
```


As observed from 1) the individual ts are non-stationary so hence the 3 store aggregate for the 3 ts will be non-stationary as well
Confirming stationarity with KPSS test

Null hypo in KPSS is that data is stationary
If p<0.05, null hypothesis is rejected

```{r}
kpss.test(Store_CA_1[,"store_1"])
kpss.test(Store_CA_2[,"store_2"])
kpss.test(Store_CA_3[,"store_3"])

#All three values are non-stationary
#So,considering differentiated version of the time series to progress and fit with multivariate models
```

```{r}
Store_CA_1_diff<-diff(Store_CA_1,lag=1)
Store_CA_2_diff<-diff(Store_CA_2,lag=1)
Store_CA_3_diff<-diff(Store_CA_3,lag=1)
Store_CA_1_diff<-Store_CA_1_diff[-1]
Store_CA_2_diff<-Store_CA_2_diff[-1]
Store_CA_3_diff<-Store_CA_3_diff[-1]
```
#All three values are non-stationary
#So,considering differentiated version of the time series to progress and fit with multivariate models
#Now let us convert the original features into stationary ones we can use for the multivar model

```{r}
Hobbies_1_diff<-diff(tsdata$Hobbies_CA_1,lag=1)
Hobbies_1_diff<-Hobbies_1_diff[-1]

Hobbies_2_diff<-diff(tsdata$Hobbies_CA_2,lag=1)
Hobbies_2_diff<-Hobbies_2_diff[-1]


Hobbies_3_diff<-diff(tsdata$Hobbies_CA_3,lag=1)
Hobbies_3_diff<-Hobbies_3_diff[-1]

Household_1_CA_1_diff<-diff(tsdata$Household_1_CA_1,lag=1)
Household_1_CA_1_diff<-Household_1_CA_1_diff[-1]
  
Household_2_CA_1_diff<-diff(tsdata$Household_2_CA_1,lag=1)
Household_2_CA_1_diff<-Household_2_CA_1_diff[-1]
  
Household_1_CA_2_diff<-diff(tsdata$Household_1_CA_2,lag=1)
Household_1_CA_2_diff<-Household_1_CA_2_diff[-1]

Household_2_CA_2_diff<-diff(tsdata$Household_2_CA_2,lag=1)
Household_2_CA_2_diff<-Household_2_CA_2_diff[-1]
  
Household_1_CA_3_diff<-diff(tsdata$Household_1_CA_3,lag=1)
Household_1_CA_3_diff<-Household_1_CA_3_diff[-1]

Household_2_CA_3_diff<-diff(tsdata$Household_2_CA_3,lag=1)
Household_2_CA_3_diff<-Household_2_CA_3_diff[-1]
  
Foods_1_CA_1_diff<-diff(tsdata$Foods_1_CA_1,lag=1)
Foods_1_CA_1_diff<-Foods_1_CA_1_diff[-1]


Foods_2_CA_1_diff<-diff(tsdata$Foods_2_CA_1,lag=1)
Foods_2_CA_1_diff<-Foods_2_CA_1_diff[-1]

Foods_3_CA_1_diff<-diff(tsdata$Foods_3_CA_1,lag=1)
Foods_3_CA_1_diff<-Foods_3_CA_1_diff[-1]

Foods_1_CA_2_diff<-diff(tsdata$Foods_1_CA_2,lag=1)
Foods_1_CA_2_diff<-Foods_1_CA_2_diff[-1]


Foods_2_CA_2_diff<-diff(tsdata$Foods_2_CA_2,lag=1)
Foods_2_CA_2_diff<-Foods_2_CA_2_diff[-1]

Foods_3_CA_2_diff<-diff(tsdata$Foods_3_CA_2,lag=1)
Foods_3_CA_2_diff<-Foods_3_CA_2_diff[-1]

Foods_1_CA_3_diff<-diff(tsdata$Foods_1_CA_3,lag=1)
Foods_1_CA_3_diff<-Foods_1_CA_3_diff[-1]


Foods_2_CA_3_diff<-diff(tsdata$Foods_2_CA_3,lag=1)
Foods_2_CA_3_diff<-Foods_2_CA_3_diff[-1]

Foods_3_CA_3_diff<-diff(tsdata$Foods_3_CA_3,lag=1)
Foods_3_CA_3_diff<-Foods_3_CA_3_diff[-1]


```


```{r}
correl_ts<-cbind(Store_CA_1_diff,Store_CA_2_diff,Store_CA_3_diff,Hobbies_1_diff,Hobbies_2_diff,Hobbies_3_diff,Household_1_CA_1_diff,Household_2_CA_1_diff,Household_1_CA_2_diff,Household_2_CA_2_diff,Household_1_CA_3_diff,Household_2_CA_3_diff,Foods_1_CA_1_diff, Foods_2_CA_1_diff, Foods_3_CA_1_diff, Foods_1_CA_2_diff, Foods_2_CA_2_diff, Foods_3_CA_2_diff, Foods_1_CA_3_diff, Foods_2_CA_3_diff, Foods_3_CA_3_diff)
corrplot(cor(correl_ts),method = 'square',title = "Store aggregate vs individual features",  addCoef.col = 'black', tl.pos = 'lt',sig.level = 0.02, tl.cex	=0.8, cl.pos = 'n', col = COL2('PiYG'),tl.col="black",diag = TRUE)
```

#Now let us consider making a multivariate model by picking the highest correlation pairs of each store

#For store 1, highest correlation is with Foods_3_CA_1 feature(0.98)
```{r}
st1data<-cbind(Store_CA_1_diff,Foods_3_CA_1_diff)
```

#split: 80-20
```{r}
sttrain1 <- head(st1data, 1574)
sttest1 <- tail(st1data, 394)
```

#figuring out best lag
#constructing the best VAR model for the most suitable lag
```{r}
lag_st1 = VARselect(sttrain1, lag.max =12)
lag_st1$selection
Store_1_VARmodel<-VAR(sttrain1,p=12,type='both')
summary(Store_1_VARmodel)
```

#Predictions
#Predicting same length as test set
```{r}
store_predict_1<-predict(Store_1_VARmodel,n.ahead = 394) 
store_fitting_1<-fitted(Store_1_VARmodel)
store_outcome_1 <- structure(list(mean=store_predict_1$fcst[[1]][,"fcst"], x=sttrain1[,1], fitted=c(NA,NA,store_fitting_1[,1])),class="forecast")
print(accuracy(store_outcome_1,sttest1[,1]))
```

#For store 2, highest correlation is with Foods_3_CA_2 feature(0.9)
```{r}
st2data<-cbind(Store_CA_2_diff,Foods_3_CA_2_diff)
sttrain2 <- head(st2data, 1574)
sttest2 <- tail(st2data, 394)
```

#figuring out best lag
```{r}
lag_st2 = VARselect(sttrain2, lag.max =12)
lag_st2$selection
```

#constructing the best VAR model for the most suitable lag
```{r}
Store_2_VARmodel<-VAR(sttrain2,p=12,type='both')
summary(Store_2_VARmodel)
```

#Predictions
#Predicting same length as test set
```{r}
store_predict_2<-predict(Store_2_VARmodel,n.ahead = 394) 
store_fitting_2<-fitted(Store_2_VARmodel)
store_outcome_2 <- structure(list(mean=store_predict_2$fcst[[1]][,"fcst"], x=sttrain2[,1], fitted=c(NA,NA,store_fitting_2[,1])),class="forecast")
print(accuracy(store_outcome_2,sttest1[,1]))
```

#For store 3, highest correlation is with Foods_3_CA_3 feature(0.98)
```{r}
st3data<-cbind(Store_CA_3_diff,Foods_3_CA_3_diff)
sttrain3 <- head(st3data, 1574)
sttest3 <- tail(st3data, 394)

```

#figuring out best lag
```{r}
lag_st2 = VARselect(sttrain3, lag.max =12)
lag_st2$selection
```

#constructing the best VAR model for the most suitable lag
```{r}
Store_3_VARmodel<-VAR(sttrain3,p=12,type='both')
summary(Store_3_VARmodel)
```

#Predictions
#Predicting same length as test set
```{r}
store_predict_3<-predict(Store_3_VARmodel,n.ahead = 394) 
store_fitting_3<-fitted(Store_3_VARmodel)
store_outcome_3 <- structure(list(mean=store_predict_3$fcst[[1]][,"fcst"], x=sttrain3[,1], fitted=c(NA,NA,store_fitting_3[,1])),class="forecast")
print(accuracy(store_outcome_3,sttest1[,1]))

```

