---
title: "q1"
output: pdf_document
---
```{r setup}
library(readr)
library(forecast)
library(xts)
library(ggplot2)
library(reshape2)
library(dygraphs)
library(dplyr)
library(fpp)
library(fpp3)
library(gridExtra)
library(tidyverse)
library(timetk)
library(tseries)
# Setup for the plotly charts (# FALSE returns ggplots)
interactive <- TRUE
```

#Step 1 read the csv datasets files
```{r}
data = read.csv("/Users/yingding/Desktop/Forcasting M2/Project and data-20220107/github code/Projectdata.csv")
```

#transform to time series data
```{r}
data$date <- as.Date(data$date)  
tsdata <- xts(data[,2:19], data$date )
```


#Step 2 plot the data with acf and pacf
```{r}
for (i in 1:6){
 pardata <- tsdata[,c(i,i+6,i+12)]
 p <- dygraph(pardata)
 acf(pardata)
 pacf(pardata)
 print(p)
 }
```

#Step 3 check seasonality
```{r}
#function to plot hte decomposition
decomp.plot <- function(x, main = NULL, ...)
{
    if(is.null(main))
	main <- paste("Decomposition of", x$type, "time series")
    plot(cbind(observed = x$random + if (x$type == "additive")
        x$trend + x$seasonal
    else x$trend * x$seasonal, trend = x$trend, seasonal = x$seasonal,
        random = x$random), main = main, ...)
}

for (i in 1:18)
{
 monthdata <- ts(tsdata, frequency=12)
 seasondata<- decompose(monthdata[,i])
 decomp.plot(seasondata, main = colnames(monthdata)[i])
}

```

#Step 3 check seasonality: ADF test
```{r}
for (i in 2:18){
a <- adf.test(data[,i])
print(a)
}
```


#Stationarity test
#KPSS test
#Null hypo in KPSS is that data is stationary
#If p<0.05, null hypothesis is rejected
```{r}
#Hobbies
kpss.test(tsdata[,"Hobbies_CA_1"])
kpss.test(tsdata[,"Hobbies_CA_2"])
kpss.test(tsdata[,"Hobbies_CA_3"])

```
Hobbies show nonstationarity-reject null hypothesis 


Household
```{r}
kpss.test(tsdata[,"Household_1_CA_1"])
kpss.test(tsdata[,"Household_1_CA_2"])
kpss.test(tsdata[,"Household_1_CA_3"])

kpss.test(tsdata[,"Household_2_CA_1"])
kpss.test(tsdata[,"Household_2_CA_2"])
kpss.test(tsdata[,"Household_2_CA_3"])
```
Household_1 and Household_2 parameters show nonstationarity


```{r}
#Foods
kpss.test(tsdata[,"Foods_1_CA_1"])
kpss.test(tsdata[,"Foods_1_CA_2"])
kpss.test(tsdata[,"Foods_1_CA_3"])

kpss.test(tsdata[,"Foods_2_CA_1"])
kpss.test(tsdata[,"Foods_2_CA_2"])
kpss.test(tsdata[,"Foods_2_CA_3"])

kpss.test(tsdata[,"Foods_3_CA_1"])
kpss.test(tsdata[,"Foods_3_CA_2"])
kpss.test(tsdata[,"Foods_3_CA_3"])

```
Foods_1,2 and 3 parameters show nonstationarity


Summary of analysis: by checking both the graphs and stationary test, all the time series show nonstationary and they have both the seasonal and trend part. 

