---
title: "Q1.5b"
output:
  pdf_document: default
  html_document: default
---


```{r setup, include=FALSE}
## Load necessary libraries
library(readr)
library(forecast)
library(xts)
getwd()
library(dplyr)
library(fpp)
library(fpp3)
library(gridExtra)
library(ggplot2)
library(ranger)
library(ftsa)
library(Metrics)
library(smooth)
library(Mcomp)
library(rmarkdown)
library(fable)


## Load environments

#Load the environment variables from q1.5a and Q1.3
load("myEnvironment_Q3.RData")
load("myEnvironment_Q1.5a.RData")


#Number of variables
nvar = 18

Split_1_daily = list(Methods_Hobb_CA1_Sp1, Methods_Hobb_CA2_Sp1, Methods_Hobb_CA3_Sp1, Methods_House1_CA1_Sp1, Methods_House1_CA2_Sp1, Methods_House1_CA3_Sp1, Methods_House2_CA1_Sp1, Methods_House2_CA2_Sp1, Methods_House2_CA3_Sp1, Methods_Foods1_CA1_Sp1, Methods_Foods1_CA2_Sp1, Methods_Foods1_CA3_Sp1, Methods_Foods2_CA1_Sp1, Methods_Foods2_CA2_Sp1, Methods_Foods2_CA3_Sp1, Methods_Foods3_CA1_Sp1, Methods_Foods3_CA2_Sp1, Methods_Foods3_CA3_Sp1)


Split_1_weekly = list(Methods_Q5_Hobb_CA1_Sp1, Methods_Q5_Hobb_CA2_Sp1, Methods_Q5_Hobb_CA3_Sp1, Methods_Q5_House1_CA1_Sp1, Methods_Q5_House1_CA2_Sp1, Methods_Q5_House1_CA3_Sp1, Methods_Q5_House2_CA1_Sp1, Methods_Q5_House2_CA2_Sp1, Methods_Q5_House2_CA3_Sp1, Methods_Q5_Foods1_CA1_Sp1, Methods_Q5_Foods1_CA2_Sp1, Methods_Q5_Foods1_CA3_Sp1, Methods_Q5_Foods2_CA1_Sp1, Methods_Q5_Foods2_CA2_Sp1, Methods_Q5_Foods2_CA3_Sp1, Methods_Q5_Foods3_CA1_Sp1, Methods_Q5_Foods3_CA2_Sp1, Methods_Q5_Foods3_CA3_Sp1)

ts = xts(Methods_Foods1_CA2_Sp2[,1:10],as.Date(data[1379:1406, ]$date))

var_names <- c('Hobbies_CA_1', 'Hobbies_CA_2', 'Hobbies_CA_3',  'Household_1_CA_1', 'Household_1_CA_2', 'Household_1_CA_3', 'Household_2_CA_1', 'Household_2_CA_2', 'Household_2_CA_3', "Foods_1_CA_1", 'Foods_1_CA_2', 'Foods_1_CA_3', "Foods_2_CA_1", 'Foods_2_CA_2', 'Foods_2_CA_3', "Foods_3_CA_1", 'Foods_3_CA_2', 'Foods_3_CA_3')


# Create empty dataframe
mat = matrix(ncol = 3, nrow =18)
naivedf = data.frame(mat)
snaivedf = data.frame(mat)
madf = data.frame(mat)
esdf = data.frame(mat)
esxdf = data.frame(mat)
arimadf = data.frame(mat)
sarimadf = data.frame(mat)
sarimaxdf = data.frame(mat)
hwdf = data.frame(mat)
ssmdf = data.frame(mat)
```


The tables shown below present the RMSSE values for the different forecasting methods and compares their accuracy for both weekly forecasts and weekly aggregates of daily forecasts.



##First split - 70/30
For the first split
Split 1 - Naive forecasts
```{r , echo=FALSE}
m = 1

for (v in 1:length(var_names)){
    series_daily = Split_1_daily[[v]]
    ts = xts(series_daily,as.Date(data[1382:1409, ]$date))
    ts_daily = as.xts(ts)
    ts_daily_weekly = apply.weekly(ts_daily[,1:10], colSums)
    actuals = as.numeric(head(test1[,v], 4))
    predictions_daily = as.numeric(head(ts_daily_weekly[,m], 4))
    predictions_weekly = as.numeric(head(Split_1_weekly[[v]][,m], 4))
    naivedf[v,1] = RMSSE(actuals, predictions_weekly, 0.5)
    naivedf[v,2] = RMSSE(actuals, predictions_daily, 0.5)
}

colnames(naivedf) = c("Weekly", "Daily_agg", "Best")
rownames(naivedf) = var_names

for (r in 1:nrow(naivedf)){
    naivedf[r,3] = ifelse(naivedf[r,1] > naivedf[r,2], "Daily agg.", "Weekly")

}

naivedf
```

Split 1 - sNaive forecasts
```{r , echo=FALSE}
m = 2

for (v in 1:length(var_names)){
    series_daily = Split_1_daily[[v]]
    ts = xts(series_daily,as.Date(data[1382:1409, ]$date))
    ts_daily = as.xts(ts)
    ts_daily_weekly = apply.weekly(ts_daily[,1:10], colSums)
    actuals = as.numeric(head(test1[,v], 4))
    predictions_daily = as.numeric(head(ts_daily_weekly[,m], 4))
    predictions_weekly = as.numeric(head(Split_1_weekly[[v]][,m], 4))
    snaivedf[v,1] = RMSSE(actuals, predictions_weekly, 0.5)
    snaivedf[v,2] = RMSSE(actuals, predictions_daily, 0.5)
}

colnames(snaivedf) = c("Weekly", "Daily_agg", "Best")
rownames(snaivedf) = var_names

for (r in 1:nrow(snaivedf)){
    snaivedf[r,3] = ifelse(snaivedf[r,1] > snaivedf[r,2], "Daily agg.", "Weekly")

}

snaivedf
```


Split 1 - MA forecasts
```{r , echo=FALSE}
m = 3

for (v in 1:length(var_names)){
    series_daily = Split_1_daily[[v]]
    ts = xts(series_daily,as.Date(data[1382:1409, ]$date))
    ts_daily = as.xts(ts)
    ts_daily_weekly = apply.weekly(ts_daily[,1:10], colSums)
    actuals = as.numeric(head(test1[,v], 4))
    predictions_daily = as.numeric(head(ts_daily_weekly[,m], 4))
    predictions_weekly = as.numeric(head(Split_1_weekly[[v]][,m], 4))
    madf[v,1] = RMSSE(actuals, predictions_weekly, 0.5)
    madf[v,2] = RMSSE(actuals, predictions_daily, 0.5)
}

colnames(madf) = c("Weekly", "Daily_agg", "Best")
rownames(madf) = var_names

for (r in 1:nrow(madf)){
    madf[r,3] = ifelse(madf[r,1] > madf[r,2], "Daily agg.", "Weekly")

}

madf
```


Split 1 - ES forecasts
```{r , echo=FALSE}
m = 4

for (v in 1:length(var_names)){
    series_daily = Split_1_daily[[v]]
    ts = xts(series_daily,as.Date(data[1382:1409, ]$date))
    ts_daily = as.xts(ts)
    ts_daily_weekly = apply.weekly(ts_daily[,1:10], colSums)
    actuals = as.numeric(head(test1[,v], 4))
    predictions_daily = as.numeric(head(ts_daily_weekly[,m], 4))
    predictions_weekly = as.numeric(head(Split_1_weekly[[v]][,m], 4))
    esdf[v,1] = RMSSE(actuals, predictions_weekly, 0.5)
    esdf[v,2] = RMSSE(actuals, predictions_daily, 0.5)
}

colnames(esdf) = c("Weekly", "Daily_agg", "Best")
rownames(esdf) = var_names

for (r in 1:nrow(esdf)){
    esdf[r,3] = ifelse(esdf[r,1] > esdf[r,2], "Daily agg.", "Weekly")

}

esdf
```


Split 1 - ESX forecasts
```{r , echo=FALSE}
m = 5

for (v in 1:length(var_names)){
    series_daily = Split_1_daily[[v]]
    ts = xts(series_daily,as.Date(data[1382:1409, ]$date))
    ts_daily = as.xts(ts)
    ts_daily_weekly = apply.weekly(ts_daily[,1:10], colSums)
    actuals = as.numeric(head(test1[,v], 4))
    predictions_daily = as.numeric(head(ts_daily_weekly[,m], 4))
    predictions_weekly = as.numeric(head(Split_1_weekly[[v]][,m], 4))
    esxdf[v,1] = RMSSE(actuals, predictions_weekly, 0.5)
    esxdf[v,2] = RMSSE(actuals, predictions_daily, 0.5)
}

colnames(esxdf) = c("Weekly", "Daily_agg", "Best")
rownames(esxdf) = var_names

for (r in 1:nrow(esxdf)){
    esxdf[r,3] = ifelse(esxdf[r,1] > esxdf[r,2], "Daily agg.", "Weekly")

}

esxdf
```


Split 1 - ARIMA forecasts
```{r , echo=FALSE}
m = 6

for (v in 1:length(var_names)){
    series_daily = Split_1_daily[[v]]
    ts = xts(series_daily,as.Date(data[1382:1409, ]$date))
    ts_daily = as.xts(ts)
    ts_daily_weekly = apply.weekly(ts_daily[,1:10], colSums)
    actuals = as.numeric(head(test1[,v], 4))
    predictions_daily = as.numeric(head(ts_daily_weekly[,m], 4))
    predictions_weekly = as.numeric(head(Split_1_weekly[[v]][,m], 4))
    arimadf[v,1] = RMSSE(actuals, predictions_weekly, 0.5)
    arimadf[v,2] = RMSSE(actuals, predictions_daily, 0.5)
}

colnames(arimadf) = c("Weekly", "Daily_agg", "Best")
rownames(arimadf) = var_names

for (r in 1:nrow(arimadf)){
    arimadf[r,3] = ifelse(arimadf[r,1] > arimadf[r,2], "Daily agg.", "Weekly")

}

arimadf
```


Split 1 - SARIMA forecasts
```{r , echo=FALSE}
m = 7

for (v in 1:length(var_names)){
    series_daily = Split_1_daily[[v]]
    ts = xts(series_daily,as.Date(data[1382:1409, ]$date))
    ts_daily = as.xts(ts)
    ts_daily_weekly = apply.weekly(ts_daily[,1:10], colSums)
    actuals = as.numeric(head(test1[,v], 4))
    predictions_daily = as.numeric(head(ts_daily_weekly[,m], 4))
    predictions_weekly = as.numeric(head(Split_1_weekly[[v]][,m], 4))
    sarimadf[v,1] = RMSSE(actuals, predictions_weekly, 0.5)
    sarimadf[v,2] = RMSSE(actuals, predictions_daily, 0.5)
}

colnames(sarimadf) = c("Weekly", "Daily_agg", "Best")
rownames(sarimadf) = var_names

for (r in 1:nrow(sarimadf)){
    sarimadf[r,3] = ifelse(sarimadf[r,1] > sarimadf[r,2], "Daily agg.", "Weekly")

}

sarimadf
```

Split 1 - SARIMAX forecasts
```{r , echo=FALSE}
m = 8

for (v in 1:length(var_names)){
    series_daily = Split_1_daily[[v]]
    ts = xts(series_daily,as.Date(data[1382:1409, ]$date))
    ts_daily = as.xts(ts)
    ts_daily_weekly = apply.weekly(ts_daily[,1:10], colSums)
    actuals = as.numeric(head(test1[,v], 4))
    predictions_daily = as.numeric(head(ts_daily_weekly[,m], 4))
    predictions_weekly = as.numeric(head(Split_1_weekly[[v]][,m], 4))
    sarimaxdf[v,1] = RMSSE(actuals, predictions_weekly, 0.5)
    sarimaxdf[v,2] = RMSSE(actuals, predictions_daily, 0.5)
}

colnames(sarimaxdf) = c("Weekly", "Daily_agg", "Best")
rownames(sarimaxdf) = var_names

for (r in 1:nrow(sarimaxdf)){
    sarimaxdf[r,3] = ifelse(sarimaxdf[r,1] > sarimaxdf[r,2], "Daily agg.", "Weekly")

}

sarimaxdf
```



Split 1 - Holt-Winters forecasts
```{r , echo=FALSE}
m = 9

for (v in 1:length(var_names)){
    series_daily = Split_1_daily[[v]]
    ts = xts(series_daily,as.Date(data[1382:1409, ]$date))
    ts_daily = as.xts(ts)
    ts_daily_weekly = apply.weekly(ts_daily[,1:10], colSums)
    actuals = as.numeric(head(test1[,v], 4))
    predictions_daily = as.numeric(head(ts_daily_weekly[,m], 4))
    predictions_weekly = as.numeric(head(Split_1_weekly[[v]][,m], 4))
    hwdf[v,1] = RMSSE(actuals, predictions_weekly, 0.5)
    hwdf[v,2] = RMSSE(actuals, predictions_daily, 0.5)
}

colnames(hwdf) = c("Weekly", "Daily_agg", "Best")
rownames(hwdf) = var_names

for (r in 1:nrow(hwdf)){
    hwdf[r,3] = ifelse(hwdf[r,1] > hwdf[r,2], "Daily agg.", "Weekly")

}

hwdf
```


Split 1 - State-Space Model forecasts
```{r , echo=FALSE}
m = 10

for (v in 1:length(var_names)){
    series_daily = Split_1_daily[[v]]
    ts = xts(series_daily,as.Date(data[1382:1409, ]$date))
    ts_daily = as.xts(ts)
    ts_daily_weekly = apply.weekly(ts_daily[,1:10], colSums)
    actuals = as.numeric(head(test1[,v], 4))
    predictions_daily = as.numeric(head(ts_daily_weekly[,m], 4))
    predictions_weekly = as.numeric(head(Split_1_weekly[[v]][,m], 4))
    ssmdf[v,1] = RMSSE(actuals, predictions_weekly, 0.5)
    ssmdf[v,2] = RMSSE(actuals, predictions_daily, 0.5)
}

colnames(ssmdf) = c("Weekly", "Daily_agg", "Best")
rownames(ssmdf) = var_names

for (r in 1:nrow(ssmdf)){
    ssmdf[r,3] = ifelse(ssmdf[r,1] > ssmdf[r,2], "Daily agg.", "Weekly")

}

ssmdf
```


##Second split - 80/20
For the second split
```{r , echo=FALSE}
#Number of variables
nvar = 18

Split_2_daily = list(Methods_Hobb_CA1_Sp2, Methods_Hobb_CA2_Sp2, Methods_Hobb_CA3_Sp2, Methods_House1_CA1_Sp2, Methods_House1_CA2_Sp2, Methods_House1_CA3_Sp2, Methods_House2_CA1_Sp2, Methods_House2_CA2_Sp2, Methods_House2_CA3_Sp2, Methods_Foods1_CA1_Sp2, Methods_Foods1_CA2_Sp2, Methods_Foods1_CA3_Sp2, Methods_Foods2_CA1_Sp2, Methods_Foods2_CA2_Sp2, Methods_Foods2_CA3_Sp2, Methods_Foods3_CA1_Sp2, Methods_Foods3_CA2_Sp2, Methods_Foods3_CA3_Sp2)


Split_2_weekly = list(Methods_Q5_Hobb_CA1_Sp2, Methods_Q5_Hobb_CA2_Sp2, Methods_Q5_Hobb_CA3_Sp2, Methods_Q5_House1_CA1_Sp2, Methods_Q5_House1_CA2_Sp2, Methods_Q5_House1_CA3_Sp2, Methods_Q5_House2_CA1_Sp2, Methods_Q5_House2_CA2_Sp2, Methods_Q5_House2_CA3_Sp2, Methods_Q5_Foods1_CA1_Sp2, Methods_Q5_Foods1_CA2_Sp2, Methods_Q5_Foods1_CA3_Sp2, Methods_Q5_Foods2_CA1_Sp2, Methods_Q5_Foods2_CA2_Sp2, Methods_Q5_Foods2_CA3_Sp2, Methods_Q5_Foods3_CA1_Sp2, Methods_Q5_Foods3_CA2_Sp2, Methods_Q5_Foods3_CA3_Sp2)

ts = xts(Methods_Foods1_CA2_Sp2[,1:10],as.Date(data[1379:1406, ]$date))

var_names <- c('Hobbies_CA_1', 'Hobbies_CA_2', 'Hobbies_CA_3',  'Household_1_CA_1', 'Household_1_CA_2', 'Household_1_CA_3', 'Household_2_CA_1', 'Household_2_CA_2', 'Household_2_CA_3', "Foods_1_CA_1", 'Foods_1_CA_2', 'Foods_1_CA_3', "Foods_2_CA_1", 'Foods_2_CA_2', 'Foods_2_CA_3', "Foods_3_CA_1", 'Foods_3_CA_2', 'Foods_3_CA_3')


# Create empty dataframe
mat = matrix(ncol = 3, nrow =18)
naivedf = data.frame(mat)
snaivedf = data.frame(mat)
madf = data.frame(mat)
esdf = data.frame(mat)
esxdf = data.frame(mat)
arimadf = data.frame(mat)
sarimadf = data.frame(mat)
sarimaxdf = data.frame(mat)
hwdf = data.frame(mat)
ssmdf = data.frame(mat)
```


Split 2 - Naive forecasts
```{r , echo=FALSE}
m = 1

for (v in 1:length(var_names)){
    series_daily = Split_2_daily[[v]]
    ts = xts(series_daily,as.Date(data[1579:1606, ]$date))
    ts_daily = as.xts(ts)
    ts_daily_weekly = apply.weekly(ts_daily[,1:10], colSums)
    actuals = as.numeric(head(test1[,v], 4))
    predictions_daily = as.numeric(head(ts_daily_weekly[,m], 4))
    predictions_weekly = as.numeric(head(Split_2_weekly[[v]][,m], 4))
    naivedf[v,1] = RMSSE(actuals, predictions_weekly, 0.5)
    naivedf[v,2] = RMSSE(actuals, predictions_daily, 0.5)
}

colnames(naivedf) = c("Weekly", "Daily_agg", "Best")
rownames(naivedf) = var_names

for (r in 1:nrow(naivedf)){
    naivedf[r,3] = ifelse(naivedf[r,1] > naivedf[r,2], "Daily agg.", "Weekly")

}

naivedf
```


Split 2 - sNaive forecasts
```{r , echo=FALSE}
m = 2

for (v in 1:length(var_names)){
    series_daily = Split_2_daily[[v]]
    ts = xts(series_daily,as.Date(data[1579:1606, ]$date))
    ts_daily = as.xts(ts)
    ts_daily_weekly = apply.weekly(ts_daily[,1:10], colSums)
    actuals = as.numeric(head(test1[,v], 4))
    predictions_daily = as.numeric(head(ts_daily_weekly[,m], 4))
    predictions_weekly = as.numeric(head(Split_2_weekly[[v]][,m], 4))
    snaivedf[v,1] = RMSSE(actuals, predictions_weekly, 0.5)
    snaivedf[v,2] = RMSSE(actuals, predictions_daily, 0.5)
}

colnames(snaivedf) = c("Weekly", "Daily_agg", "Best")
rownames(snaivedf) = var_names

for (r in 1:nrow(snaivedf)){
    snaivedf[r,3] = ifelse(snaivedf[r,1] > snaivedf[r,2], "Daily agg.", "Weekly")

}

snaivedf
```


Split 2 - MA forecasts
```{r , echo=FALSE}
m = 3

for (v in 1:length(var_names)){
    series_daily = Split_2_daily[[v]]
    ts = xts(series_daily,as.Date(data[1579:1606, ]$date))
    ts_daily = as.xts(ts)
    ts_daily_weekly = apply.weekly(ts_daily[,1:10], colSums)
    actuals = as.numeric(head(test1[,v], 4))
    predictions_daily = as.numeric(head(ts_daily_weekly[,m], 4))
    predictions_weekly = as.numeric(head(Split_2_weekly[[v]][,m], 4))
    madf[v,1] = RMSSE(actuals, predictions_weekly, 0.5)
    madf[v,2] = RMSSE(actuals, predictions_daily, 0.5)
}

colnames(madf) = c("Weekly", "Daily_agg", "Best")
rownames(madf) = var_names

for (r in 1:nrow(madf)){
    madf[r,3] = ifelse(madf[r,1] > madf[r,2], "Daily agg.", "Weekly")

}

madf
```

Split 2 - ES forecasts
```{r , echo=FALSE}
m = 4

for (v in 1:length(var_names)){
    series_daily = Split_2_daily[[v]]
    ts = xts(series_daily,as.Date(data[1579:1606, ]$date))
    ts_daily = as.xts(ts)
    ts_daily_weekly = apply.weekly(ts_daily[,1:10], colSums)
    actuals = as.numeric(head(test1[,v], 4))
    predictions_daily = as.numeric(head(ts_daily_weekly[,m], 4))
    predictions_weekly = as.numeric(head(Split_2_weekly[[v]][,m], 4))
    esdf[v,1] = RMSSE(actuals, predictions_weekly, 0.5)
    esdf[v,2] = RMSSE(actuals, predictions_daily, 0.5)
}

colnames(esdf) = c("Weekly", "Daily_agg", "Best")
rownames(esdf) = var_names

for (r in 1:nrow(esdf)){
    esdf[r,3] = ifelse(esdf[r,1] > esdf[r,2], "Daily agg.", "Weekly")

}

esdf
```

Split 2 - ESX forecasts
```{r , echo=FALSE}
m = 5

for (v in 1:length(var_names)){
    series_daily = Split_2_daily[[v]]
    ts = xts(series_daily,as.Date(data[1579:1606, ]$date))
    ts_daily = as.xts(ts)
    ts_daily_weekly = apply.weekly(ts_daily[,1:10], colSums)
    actuals = as.numeric(head(test1[,v], 4))
    predictions_daily = as.numeric(head(ts_daily_weekly[,m], 4))
    predictions_weekly = as.numeric(head(Split_2_weekly[[v]][,m], 4))
    esxdf[v,1] = RMSSE(actuals, predictions_weekly, 0.5)
    esxdf[v,2] = RMSSE(actuals, predictions_daily, 0.5)
}

colnames(esxdf) = c("Weekly", "Daily_agg", "Best")
rownames(esxdf) = var_names

for (r in 1:nrow(esxdf)){
    esxdf[r,3] = ifelse(esxdf[r,1] > esxdf[r,2], "Daily agg.", "Weekly")

}

esxdf
```


Split 2 - ARIMA forecasts
```{r , echo=FALSE}
m = 6

for (v in 1:length(var_names)){
    series_daily = Split_2_daily[[v]]
    ts = xts(series_daily,as.Date(data[1579:1606, ]$date))
    ts_daily = as.xts(ts)
    ts_daily_weekly = apply.weekly(ts_daily[,1:10], colSums)
    actuals = as.numeric(head(test1[,v], 4))
    predictions_daily = as.numeric(head(ts_daily_weekly[,m], 4))
    predictions_weekly = as.numeric(head(Split_2_weekly[[v]][,m], 4))
    arimadf[v,1] = RMSSE(actuals, predictions_weekly, 0.5)
    arimadf[v,2] = RMSSE(actuals, predictions_daily, 0.5)
}

colnames(arimadf) = c("Weekly", "Daily_agg", "Best")
rownames(arimadf) = var_names

for (r in 1:nrow(arimadf)){
    arimadf[r,3] = ifelse(arimadf[r,1] > arimadf[r,2], "Daily agg.", "Weekly")

}

arimadf
```


Split 2 - SARIMA forecasts
```{r , echo=FALSE}
m = 7

for (v in 1:length(var_names)){
    series_daily = Split_2_daily[[v]]
    ts = xts(series_daily,as.Date(data[1579:1606, ]$date))
    ts_daily = as.xts(ts)
    ts_daily_weekly = apply.weekly(ts_daily[,1:10], colSums)
    actuals = as.numeric(head(test1[,v], 4))
    predictions_daily = as.numeric(head(ts_daily_weekly[,m], 4))
    predictions_weekly = as.numeric(head(Split_2_weekly[[v]][,m], 4))
    sarimadf[v,1] = RMSSE(actuals, predictions_weekly, 0.5)
    sarimadf[v,2] = RMSSE(actuals, predictions_daily, 0.5)
}

colnames(sarimadf) = c("Weekly", "Daily_agg", "Best")
rownames(sarimadf) = var_names

for (r in 1:nrow(sarimadf)){
    sarimadf[r,3] = ifelse(sarimadf[r,1] > sarimadf[r,2], "Daily agg.", "Weekly")

}

sarimadf
```


Split 2 - SARIMAX forecasts
```{r , echo=FALSE}
m = 8

for (v in 1:length(var_names)){
    series_daily = Split_2_daily[[v]]
    ts = xts(series_daily,as.Date(data[1579:1606, ]$date))
    ts_daily = as.xts(ts)
    ts_daily_weekly = apply.weekly(ts_daily[,1:10], colSums)
    actuals = as.numeric(head(test1[,v], 4))
    predictions_daily = as.numeric(head(ts_daily_weekly[,m], 4))
    predictions_weekly = as.numeric(head(Split_2_weekly[[v]][,m], 4))
    sarimaxdf[v,1] = RMSSE(actuals, predictions_weekly, 0.5)
    sarimaxdf[v,2] = RMSSE(actuals, predictions_daily, 0.5)
}

colnames(sarimaxdf) = c("Weekly", "Daily_agg", "Best")
rownames(sarimaxdf) = var_names

for (r in 1:nrow(sarimaxdf)){
    sarimaxdf[r,3] = ifelse(sarimaxdf[r,1] > sarimaxdf[r,2], "Daily agg.", "Weekly")

}

sarimaxdf
```


Split 2 - Holt-Winters forecasts
```{r , echo=FALSE}
m = 9

for (v in 1:length(var_names)){
    series_daily = Split_2_daily[[v]]
    ts = xts(series_daily,as.Date(data[1579:1606, ]$date))
    ts_daily = as.xts(ts)
    ts_daily_weekly = apply.weekly(ts_daily[,1:10], colSums)
    actuals = as.numeric(head(test1[,v], 4))
    predictions_daily = as.numeric(head(ts_daily_weekly[,m], 4))
    predictions_weekly = as.numeric(head(Split_2_weekly[[v]][,m], 4))
    hwdf[v,1] = RMSSE(actuals, predictions_weekly, 0.5)
    hwdf[v,2] = RMSSE(actuals, predictions_daily, 0.5)
}

colnames(hwdf) = c("Weekly", "Daily_agg", "Best")
rownames(hwdf) = var_names

for (r in 1:nrow(hwdf)){
    hwdf[r,3] = ifelse(hwdf[r,1] > hwdf[r,2], "Daily agg.", "Weekly")

}

hwdf
```


Split 2 - State-Space Model forecasts
```{r , echo=FALSE}
m = 10

for (v in 1:length(var_names)){
    series_daily = Split_2_daily[[v]]
    ts = xts(series_daily,as.Date(data[1579:1606, ]$date))
    ts_daily = as.xts(ts)
    ts_daily_weekly = apply.weekly(ts_daily[,1:10], colSums)
    actuals = as.numeric(head(test1[,v], 4))
    predictions_daily = as.numeric(head(ts_daily_weekly[,m], 4))
    predictions_weekly = as.numeric(head(Split_2_weekly[[v]][,m], 4))
    ssmdf[v,1] = RMSSE(actuals, predictions_weekly, 0.5)
    ssmdf[v,2] = RMSSE(actuals, predictions_daily, 0.5)
}

colnames(ssmdf) = c("Weekly", "Daily_agg", "Best")
rownames(ssmdf) = var_names

for (r in 1:nrow(ssmdf)){
    ssmdf[r,3] = ifelse(ssmdf[r,1] > ssmdf[r,2], "Daily agg.", "Weekly")

}

ssmdf
```

##Third split - 90/10
For the third split
```{r , echo=FALSE}
#Number of variables
nvar = 18

Split_3_daily = list(Methods_Hobb_CA1_Sp3, Methods_Hobb_CA2_Sp3, Methods_Hobb_CA3_Sp3, Methods_House1_CA1_Sp3, Methods_House1_CA2_Sp3, Methods_House1_CA3_Sp3, Methods_House2_CA1_Sp3, Methods_House2_CA2_Sp3, Methods_House2_CA3_Sp3, Methods_Foods1_CA1_Sp3, Methods_Foods1_CA2_Sp3, Methods_Foods1_CA3_Sp3, Methods_Foods2_CA1_Sp3, Methods_Foods2_CA2_Sp3, Methods_Foods2_CA3_Sp3, Methods_Foods3_CA1_Sp3, Methods_Foods3_CA2_Sp3, Methods_Foods3_CA3_Sp3)


Split_3_weekly = list(Methods_Q5_Hobb_CA1_Sp3, Methods_Q5_Hobb_CA2_Sp3, Methods_Q5_Hobb_CA3_Sp3, Methods_Q5_House1_CA1_Sp3, Methods_Q5_House1_CA2_Sp3, Methods_Q5_House1_CA3_Sp3, Methods_Q5_House2_CA1_Sp3, Methods_Q5_House2_CA2_Sp3, Methods_Q5_House2_CA3_Sp3, Methods_Q5_Foods1_CA1_Sp3, Methods_Q5_Foods1_CA2_Sp3, Methods_Q5_Foods1_CA3_Sp3, Methods_Q5_Foods2_CA1_Sp3, Methods_Q5_Foods2_CA2_Sp3, Methods_Q5_Foods2_CA3_Sp3, Methods_Q5_Foods3_CA1_Sp3, Methods_Q5_Foods3_CA2_Sp3, Methods_Q5_Foods3_CA3_Sp3)

ts = xts(Methods_Foods1_CA2_Sp3[,1:10],as.Date(data[1379:1406, ]$date))

var_names <- c('Hobbies_CA_1', 'Hobbies_CA_2', 'Hobbies_CA_3',  'Household_1_CA_1', 'Household_1_CA_2', 'Household_1_CA_3', 'Household_2_CA_1', 'Household_2_CA_2', 'Household_2_CA_3', "Foods_1_CA_1", 'Foods_1_CA_2', 'Foods_1_CA_3', "Foods_2_CA_1", 'Foods_2_CA_2', 'Foods_2_CA_3', "Foods_3_CA_1", 'Foods_3_CA_2', 'Foods_3_CA_3')


# Create empty dataframe
mat = matrix(ncol = 3, nrow =18)
naivedf = data.frame(mat)
snaivedf = data.frame(mat)
madf = data.frame(mat)
esdf = data.frame(mat)
esxdf = data.frame(mat)
arimadf = data.frame(mat)
sarimadf = data.frame(mat)
sarimaxdf = data.frame(mat)
hwdf = data.frame(mat)
ssmdf = data.frame(mat)
```


Split 3 - Naive forecasts
```{r , echo=FALSE}
m = 1

for (v in 1:length(var_names)){
    series_daily = Split_3_daily[[v]]
    ts = xts(series_daily,as.Date(data[1579:1606, ]$date))
    ts_daily = as.xts(ts)
    ts_daily_weekly = apply.weekly(ts_daily[,1:10], colSums)
    actuals = as.numeric(head(test1[,v], 4))
    predictions_daily = as.numeric(head(ts_daily_weekly[,m], 4))
    predictions_weekly = as.numeric(head(Split_3_weekly[[v]][,m], 4))
    naivedf[v,1] = RMSSE(actuals, predictions_weekly, 0.5)
    naivedf[v,2] = RMSSE(actuals, predictions_daily, 0.5)
}

colnames(naivedf) = c("Weekly", "Daily_agg", "Best")
rownames(naivedf) = var_names

for (r in 1:nrow(naivedf)){
    naivedf[r,3] = ifelse(naivedf[r,1] > naivedf[r,2], "Daily agg.", "Weekly")

}

naivedf
```


Split 3 - sNaive forecasts
```{r , echo=FALSE}
m = 2

for (v in 1:length(var_names)){
    series_daily = Split_3_daily[[v]]
    ts = xts(series_daily,as.Date(data[1579:1606, ]$date))
    ts_daily = as.xts(ts)
    ts_daily_weekly = apply.weekly(ts_daily[,1:10], colSums)
    actuals = as.numeric(head(test1[,v], 4))
    predictions_daily = as.numeric(head(ts_daily_weekly[,m], 4))
    predictions_weekly = as.numeric(head(Split_3_weekly[[v]][,m], 4))
    snaivedf[v,1] = RMSSE(actuals, predictions_weekly, 0.5)
    snaivedf[v,2] = RMSSE(actuals, predictions_daily, 0.5)
}

colnames(snaivedf) = c("Weekly", "Daily_agg", "Best")
rownames(snaivedf) = var_names

for (r in 1:nrow(snaivedf)){
    snaivedf[r,3] = ifelse(snaivedf[r,1] > snaivedf[r,2], "Daily agg.", "Weekly")

}

snaivedf
```

Split 3 - MA forecasts
```{r , echo=FALSE}
m = 3

for (v in 1:length(var_names)){
    series_daily = Split_3_daily[[v]]
    ts = xts(series_daily,as.Date(data[1579:1606, ]$date))
    ts_daily = as.xts(ts)
    ts_daily_weekly = apply.weekly(ts_daily[,1:10], colSums)
    actuals = as.numeric(head(test1[,v], 4))
    predictions_daily = as.numeric(head(ts_daily_weekly[,m], 4))
    predictions_weekly = as.numeric(head(Split_3_weekly[[v]][,m], 4))
    madf[v,1] = RMSSE(actuals, predictions_weekly, 0.5)
    madf[v,2] = RMSSE(actuals, predictions_daily, 0.5)
}

colnames(madf) = c("Weekly", "Daily_agg", "Best")
rownames(madf) = var_names

for (r in 1:nrow(madf)){
    madf[r,3] = ifelse(madf[r,1] > madf[r,2], "Daily agg.", "Weekly")

}

madf
```


Split 3 - ES forecasts
```{r , echo=FALSE}
m = 4

for (v in 1:length(var_names)){
    series_daily = Split_3_daily[[v]]
    ts = xts(series_daily,as.Date(data[1579:1606, ]$date))
    ts_daily = as.xts(ts)
    ts_daily_weekly = apply.weekly(ts_daily[,1:10], colSums)
    actuals = as.numeric(head(test1[,v], 4))
    predictions_daily = as.numeric(head(ts_daily_weekly[,m], 4))
    predictions_weekly = as.numeric(head(Split_3_weekly[[v]][,m], 4))
    esdf[v,1] = RMSSE(actuals, predictions_weekly, 0.5)
    esdf[v,2] = RMSSE(actuals, predictions_daily, 0.5)
}

colnames(esdf) = c("Weekly", "Daily_agg", "Best")
rownames(esdf) = var_names

for (r in 1:nrow(esdf)){
    esdf[r,3] = ifelse(esdf[r,1] > esdf[r,2], "Daily agg.", "Weekly")

}

esdf
```

Split 3 - ESX forecasts
```{r , echo=FALSE}
m = 5

for (v in 1:length(var_names)){
    series_daily = Split_3_daily[[v]]
    ts = xts(series_daily,as.Date(data[1579:1606, ]$date))
    ts_daily = as.xts(ts)
    ts_daily_weekly = apply.weekly(ts_daily[,1:10], colSums)
    actuals = as.numeric(head(test1[,v], 4))
    predictions_daily = as.numeric(head(ts_daily_weekly[,m], 4))
    predictions_weekly = as.numeric(head(Split_3_weekly[[v]][,m], 4))
    esxdf[v,1] = RMSSE(actuals, predictions_weekly, 0.5)
    esxdf[v,2] = RMSSE(actuals, predictions_daily, 0.5)
}

colnames(esxdf) = c("Weekly", "Daily_agg", "Best")
rownames(esxdf) = var_names

for (r in 1:nrow(esxdf)){
    esxdf[r,3] = ifelse(esxdf[r,1] > esxdf[r,2], "Daily agg.", "Weekly")

}

esxdf
```


Split 3 - ARIMA forecasts
```{r , echo=FALSE}
m = 6

for (v in 1:length(var_names)){
    series_daily = Split_3_daily[[v]]
    ts = xts(series_daily,as.Date(data[1579:1606, ]$date))
    ts_daily = as.xts(ts)
    ts_daily_weekly = apply.weekly(ts_daily[,1:10], colSums)
    actuals = as.numeric(head(test1[,v], 4))
    predictions_daily = as.numeric(head(ts_daily_weekly[,m], 4))
    predictions_weekly = as.numeric(head(Split_3_weekly[[v]][,m], 4))
    arimadf[v,1] = RMSSE(actuals, predictions_weekly, 0.5)
    arimadf[v,2] = RMSSE(actuals, predictions_daily, 0.5)
}

colnames(arimadf) = c("Weekly", "Daily_agg", "Best")
rownames(arimadf) = var_names

for (r in 1:nrow(arimadf)){
    arimadf[r,3] = ifelse(arimadf[r,1] > arimadf[r,2], "Daily agg.", "Weekly")

}

arimadf
```


Split 3 - SARIMA forecasts
```{r , echo=FALSE}
m = 7

for (v in 1:length(var_names)){
    series_daily = Split_3_daily[[v]]
    ts = xts(series_daily,as.Date(data[1579:1606, ]$date))
    ts_daily = as.xts(ts)
    ts_daily_weekly = apply.weekly(ts_daily[,1:10], colSums)
    actuals = as.numeric(head(test1[,v], 4))
    predictions_daily = as.numeric(head(ts_daily_weekly[,m], 4))
    predictions_weekly = as.numeric(head(Split_3_weekly[[v]][,m], 4))
    sarimadf[v,1] = RMSSE(actuals, predictions_weekly, 0.5)
    sarimadf[v,2] = RMSSE(actuals, predictions_daily, 0.5)
}

colnames(sarimadf) = c("Weekly", "Daily_agg", "Best")
rownames(sarimadf) = var_names

for (r in 1:nrow(sarimadf)){
    sarimadf[r,3] = ifelse(sarimadf[r,1] > sarimadf[r,2], "Daily agg.", "Weekly")

}

sarimadf
```


Split 3 - SARIMAX forecasts
```{r , echo=FALSE}
m = 8

for (v in 1:length(var_names)){
    series_daily = Split_3_daily[[v]]
    ts = xts(series_daily,as.Date(data[1579:1606, ]$date))
    ts_daily = as.xts(ts)
    ts_daily_weekly = apply.weekly(ts_daily[,1:10], colSums)
    actuals = as.numeric(head(test1[,v], 4))
    predictions_daily = as.numeric(head(ts_daily_weekly[,m], 4))
    predictions_weekly = as.numeric(head(Split_3_weekly[[v]][,m], 4))
    sarimaxdf[v,1] = RMSSE(actuals, predictions_weekly, 0.5)
    sarimaxdf[v,2] = RMSSE(actuals, predictions_daily, 0.5)
}

colnames(sarimaxdf) = c("Weekly", "Daily_agg", "Best")
rownames(sarimaxdf) = var_names

for (r in 1:nrow(sarimaxdf)){
    sarimaxdf[r,3] = ifelse(sarimaxdf[r,1] > sarimaxdf[r,2], "Daily agg.", "Weekly")

}

sarimaxdf
```


Split 3 - Holt-Winters forecasts
```{r , echo=FALSE}
m = 9

for (v in 1:length(var_names)){
    series_daily = Split_3_daily[[v]]
    ts = xts(series_daily,as.Date(data[1579:1606, ]$date))
    ts_daily = as.xts(ts)
    ts_daily_weekly = apply.weekly(ts_daily[,1:10], colSums)
    actuals = as.numeric(head(test1[,v], 4))
    predictions_daily = as.numeric(head(ts_daily_weekly[,m], 4))
    predictions_weekly = as.numeric(head(Split_3_weekly[[v]][,m], 4))
    hwdf[v,1] = RMSSE(actuals, predictions_weekly, 0.5)
    hwdf[v,2] = RMSSE(actuals, predictions_daily, 0.5)
}

colnames(hwdf) = c("Weekly", "Daily_agg", "Best")
rownames(hwdf) = var_names

for (r in 1:nrow(hwdf)){
    hwdf[r,3] = ifelse(hwdf[r,1] > hwdf[r,2], "Daily agg.", "Weekly")

}

hwdf
```


Split 3 - State-Space Model forecasts
```{r , echo=FALSE}
m = 10

for (v in 1:length(var_names)){
    series_daily = Split_3_daily[[v]]
    ts = xts(series_daily,as.Date(data[1579:1606, ]$date))
    ts_daily = as.xts(ts)
    ts_daily_weekly = apply.weekly(ts_daily[,1:10], colSums)
    actuals = as.numeric(head(test1[,v], 4))
    predictions_daily = as.numeric(head(ts_daily_weekly[,m], 4))
    predictions_weekly = as.numeric(head(Split_3_weekly[[v]][,m], 4))
    ssmdf[v,1] = RMSSE(actuals, predictions_weekly, 0.5)
    ssmdf[v,2] = RMSSE(actuals, predictions_daily, 0.5)
}

colnames(ssmdf) = c("Weekly", "Daily_agg", "Best")
rownames(ssmdf) = var_names

for (r in 1:nrow(ssmdf)){
    ssmdf[r,3] = ifelse(ssmdf[r,1] > ssmdf[r,2], "Daily agg.", "Weekly")

}

ssmdf
```
